---
title: "Update in R package moonBook"
author: "Keon-Woong Moon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{moonBook_update}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA,
  message =FALSE
)
```

## Function "mytable"

Function "mytable"" produce table for descriptive analysis easily. It is most useful to make table to describe baseline charateristics common in medical research papers. 

## Basic Usage

If you are unfamiliar to package moonBook and mytable function, please see the R package `moonBook` vignette at: https://cran.r-project.org/web/packages/moonBook/vignettes/moonBook.html


## Explore a data.frame

You can use `mytable` function to explore a data.frame. 

```{r,comment=NA}
require(moonBook)
require(ztable)
require(magrittr)
options(ztable.type="html")

mytable(acs)
```

You can use formula without grouping variable(s).

```{r,comment=NA}
mytable(~age+sex,data=acs)
```


## Compress an object of class mytable

You can `compress` mytable. If rows dealing with categorical variables have two unique values, it can be printed in a single row rather than three rows.

```{r}
mytable(Dx~sex,data=acs)
```

```{r}
mytable(Dx~sex,data=acs) %>% compress
```

The default representative group is the second group. If you want the first group to being representative group, 
please use the `no` argument.


```{r}
mytable(Dx~sex,data=acs) %>% compress(no=1)
```

Sometimes it is more simple to omit the represntative group name. You can do this by set the add.label argument FALSE.

```{r}
mytable(Dx~cardiogenicShock+DM+obesity+HBP,data=acs) %>% compress
```

```{r}
mytable(Dx~cardiogenicShock+DM+obesity+HBP,data=acs) %>% compress(add.label=FALSE)
```

You can print mytable object in 'html5' or 'LaTex' format with ztable.  

```{r,results='asis'}
mytable(Dx~cardiogenicShock+DM+obesity+HBP,data=acs) %>% compress(add.label=FALSE) %>% ztable
```

## For formatted numbers: addComma()

Sometimes, you want to display formatted numbers. For example, `1234.5` can be printed as `1,234.5`.
You can do this using addComma() function

```{r}
data(diamonds,package="ggplot2")
mytable(diamonds) %>% addComma
```

Also you can print this in 'html5' or 'LaTex' format with ztable.  

```{r,results='asis'}
mytable(cut~.,data=diamonds) %>% addComma %>% ztable
```
